\huge{Meta-analytic evidence that sexual selection improves population fitness}

### 2019-04-05 Manuscripts/Manuscript_MetaAnalysis.Rmd
teep tex

---
title: '\huge{Meta-analytic evidence that sexual selection improves population fitness}'
author: 
- Justin G. Cally\textsuperscript{§*}, Devi Stuart-Fox\textsuperscript{§} and Luke Holman\textsuperscript{§}
- '\textsuperscript{§}School of BioSciences, The University of Melbourne, Parkville, VIC, 3052, Australia'
- '\textsuperscript{*}\textit{justin.g.cally@gmail.com}'
output:
  pdf_document: default
  keep_tex: yes 
bibliography: Bibliography/Bibliography.bib
subparagraph: yes
urlcolor: blue
csl: Bibliography/NComms.csl
header-includes: \usepackage{microtype} \usepackage[all]{hypcap} \usepackage{amsmath}
  \usepackage{booktabs} \usepackage{caption} \usepackage[labelfont=bf]{caption} \usepackage{titling}
  \pretitle{\begin{flushleft}\LARGE} \posttitle{\par\end{flushleft}\vskip 0.5em} \preauthor{\begin{flushleft}\large
  \lineskip 0.5em} \postauthor{\par\end{flushleft}} \predate{\begin{flushleft}\large}
  \postdate{\par\end{flushleft}} \usepackage{fancyhdr} \pagestyle{fancy} \fancyhead[LO,LE]{\textsl{\leftmark}}
  \rhead[]{Sexual selection improves fitness} \usepackage{titlefoot}
  \usepackage{amssymb} \usepackage{rotating} \usepackage{lineno} \linenumbers \usepackage{setspace}\onehalfspacing
    \usepackage{titlesec} \titleformat{\section}{\normalfont\scshape\LARGE}{\thesection}{1em}{} \titleformat{\subsection}{\normalfont\Large}{\thesubsection}{1em}{} \titleformat{\subsubsection}{\normalfont\large}{\thesubsubsection}{1em}{} \usepackage{abstract} \renewcommand{\abstractnamefont}{\normalfont\Large} 
    \usepackage{hyperref}\hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue} 
    \usepackage{color,soul}
    \raggedbottom    
abstract: Sexual selection has manifold ecological and evolutionary consequences, making its net effect on population fitness difficult to predict from first principles. Instead, one can empirically determine whether sexual selection increases or decreases population fitness by manipulating the opportunity for sexual selection in replicate populations, allow evolution to proceed, and then compare the evolved average fitness between the treatment groups. Here, we synthesise 459 effect sizes from 65 pertinent experimental evolution studies using meta-analysis. We find evidence that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females evolving under stressful conditions. However, sexual selection had weaker positive effects on direct measures of population fitness, such as extinction rate and proportion of viable offspring, than on individual fitness measures with indirect or less clear relationships to population fitness. Overall, we conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments. We discuss the implications of these results for conservation and evolutionary biology.
---
\pagestyle{plain}

>>>>

---
title: '\huge{Meta-analytic evidence that sexual selection improves population fitness}'
author: 
- Justin G. Cally\textsuperscript{§*}, Devi Stuart-Fox\textsuperscript{§} and Luke Holman\textsuperscript{§}
- '\textsuperscript{§}School of BioSciences, The University of Melbourne, Parkville, VIC, 3052, Australia'
- '\textsuperscript{*}\textit{justin.g.cally@gmail.com}'
output:
  pdf_document:
    keep_tex: true
bibliography: Bibliography/Bibliography.bib
subparagraph: yes
urlcolor: blue
csl: Bibliography/NComms.csl
header-includes: \usepackage{microtype} \usepackage[all]{hypcap} \usepackage{amsmath}
  \usepackage{booktabs} \usepackage{caption} \usepackage[labelfont=bf]{caption} \usepackage{titling}
  \pretitle{\begin{flushleft}\LARGE} \posttitle{\par\end{flushleft}\vskip 0.5em} \preauthor{\begin{flushleft}\large
  \lineskip 0.5em} \postauthor{\par\end{flushleft}} \predate{\begin{flushleft}\large}
  \postdate{\par\end{flushleft}} \usepackage{fancyhdr} \pagestyle{fancy} \fancyhead[LO,LE]{\textsl{\leftmark}}
  \rhead[]{Sexual selection improves fitness} \usepackage{titlefoot}
  \usepackage{amssymb} \usepackage{rotating} \usepackage{lineno} \linenumbers \usepackage{setspace}\onehalfspacing
    \usepackage{titlesec} \titleformat{\section}{\normalfont\scshape\LARGE}{\thesection}{1em}{} \titleformat{\subsection}{\normalfont\Large}{\thesubsection}{1em}{} \titleformat{\subsubsection}{\normalfont\large}{\thesubsubsection}{1em}{} \usepackage{abstract} \renewcommand{\abstractnamefont}{\normalfont\Large} 
    \usepackage{hyperref}\hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue} 
    \usepackage{color,soul}
    \raggedbottom    
abstract: Sexual selection has manifold ecological and evolutionary consequences, making its net effect on population fitness difficult to predict from first principles. Instead, one can empirically determine whether sexual selection increases or decreases population fitness by manipulating the opportunity for sexual selection in replicate populations, allow evolution to proceed, and then compare the evolved average fitness between the treatment groups. Here, we synthesise 459 effect sizes from 65 pertinent experimental evolution studies using meta-analysis. We find evidence that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females evolving under stressful conditions. However, sexual selection had weaker positive effects on direct measures of population fitness, such as extinction rate and proportion of viable offspring, than on individual fitness measures with indirect or less clear relationships to population fitness. Overall, we conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments. We discuss the implications of these results for conservation and evolutionary biology.
---
\pagestyle{plain}
